Visual Analysis of Ligand Trajectories in Molecular Dynamics

### 2018-09-28 paper.tex
Adams feedback on abstract

%% Abstract section.
\abstract{
In many cases, protein reactions with other small molecules (ligands) occur at a deeply buried active site.
When studying these types of reactions it is crucial for biochemists to examine trajectories of ligand motion.
These trajectories are predicted with in-silico methods that produce large ensembles of possible trajectories.
In this paper, we propose a novel approach to the interactive visual exploration and analysis of large sets of trajectories enabling domain experts to assess the relevance of individual trajectories based on their properties.
The proposed solution is composed of multiple linked 2D and 3D views, enabling the interactive exploration and filtering of trajectories in an informed way.
In the workflow, we focus on the practical aspects of the interactive visual analysis specific to ligand trajectories.
We adopt and adapt small multiples to resolve an overly large number of trajectories into smaller chunks that are easier to analyze.
We describe how drill-down techniques can be used to create and store selections of trajectories with desired properties, enabling the comparison of multiple datasets.
In appropriately crafted 2D and 3D views, biochemists can either observe individual trajectories or choose to aggregate the information into a functional boxplot or density visualization.
Our solution is based on a tight collaboration with domain experts in order to address their needs as much as possible.
The usefulness of this novel approach is demonstrated by two case studies, conducted by the collaborating protein engineers.

>>>>

%% Abstract section.
\abstract{
In many cases, protein reactions with other small molecules (ligands) occur at a deeply buried active site.
When studying these types of reactions it is crucial for biochemists to examine trajectories of ligand motion.
These trajectories are predicted with in-silico methods that produce large ensembles of possible trajectories.
In this paper, we propose a novel approach to the interactive visual exploration and analysis of large sets of ligand trajectories enabling domain experts to understand protein function based on the trajectory properties.
The proposed solution is composed of multiple linked 2D and 3D views, enabling the interactive exploration and filtering of trajectories in an informed way.
In the workflow, we focus on the practical aspects of the interactive visual analysis specific to ligand trajectories.
We adopt and adapt small multiples to resolve an overly large number of trajectories into smaller chunks that are easier to analyze.
We describe how drill-down techniques can be used to create and store selections of trajectories with desired properties, enabling the comparison of multiple datasets.
In appropriately crafted 2D and 3D views, biochemists can either observe individual trajectories or choose to aggregate the information into a functional boxplot or density visualization.
Our solution is based on a tight collaboration with domain experts in order to address their needs as much as possible.
The usefulness of this novel approach is demonstrated by two case studies, conducted by the collaborating protein engineers.
